{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2025-01-23 Notebook LaTEX/R-WAPG/paper3.tex
>w<, fixes

    The following lemma will simplifies the proof later on. 

@@

        The proof is by induction. 

@@

            To prove (ii), it remains to show that the coefficient of $x_{k + 1} - x_k$ can be expressed without $\mu, L$: 

>>>>

    The following lemma will simplify the discussion later. 

@@

@@

            To prove (ii), it remains to show that for all $k\ge 1$ the coefficient of $x_{k + 1} - x_k$ can be expressed without $\mu, L$: 
